---
title: "Non-Parametric Statistics - Problem Sets"
author: "Silvana, Florencia Luque, Simon Schmetz"
date: "2025-03-14"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Introduction

In the following document, the solutions to three problem sets from Prof. Eduardo García\-Portugués book on nonparametric Statistics (https://bookdown.org/egarpor/NP-UC3M/) as final assignment for the Course in Nonparametric Statistics at Universidad Carlos III de Madrid. 
*Contributions made to this document are made are equal among each of the three authors*


# Excercise 4.21


```{r cars}
#TODO: Silvana
```


# Excercises 5.10 
Investigate the accuracy of the naive bootstrap confidence intervals implemented in *np::npplot*. To do so:

1. Simulate $M=500$ samples of size $n =100$ from the regression model $Y=m(X)+\varepsilon$, where $m(x)=0.25x^{2}-0.75x+3$, $X\sim N(0,1.5^{2})$, and $\varepsilon \sim N(0,0.75^{2})$.

```{r,warning=FALSE}
library(np)
set.seed(1234)
M = 500
n = 100
y_muestras = matrix(0,ncol = n,nrow = M)
m = function(a){
  0.25*a^2-0.75*a+3
}
for (i in 1:500){
  x = rnorm(100,0,1.5)
  epsilon = rnorm(100,0,0.75)
  y_muestras[i,] = m(x)+epsilon
}
```

2. Compute the 95\% confidence intervals for $m(x)$  along $x\gets seq(-5, 5, by = 0.1)$, for each of the  M  samples. Do it for the normal approximation and quantile-based confidence intervals.
```{r}
x_grid = seq(-5,5,by=0.1)

```
3. Check if  $m(x)$  belongs to each of the confidence intervals, for each  x.
```{r}

```
4. Approximate the actual coverage of the confidence intervals.
```{r}

```
# Excercise 6.8

```{r}
#TODO: Simon
```


